Modelling the emergence of whisker barrels

### 2020-07-03 paper/briefpaper/brief.tex
unify spelling of organized

\cmnt{Across a wide range of parameter values, random initial conditions (a
  uniform random distribution for $a(\mb{x},0)\in(0.2,0.4)$, $c(\mb{x},0)=0$)
  eventually yielded a clear Voronoi-like tessellation of topographically
  organised thalamocortical projections, confirming that barrel maps can
  self-organise in the absence of pre-specified center points. The
  organization is apparent in a plot of the identity of the projection for
  which the connection density is maximal at each simulated cortical location,
  as shown in Fig.\,\ref{fig:main}C. Parameters for the example simulation
  shown in Fig.\,\ref{fig:main}C (see also Movie S1) were obtained by
  conducting a full parameter sweep and choosing a combination of parameter
  values ($\alpha=3.6$, $\beta=16.67$, $k=3$, $D=0.5$, $\epsilon=1.2$) that
  scored well against the following three measures.}

% New section to describe and introduce the metrics
\metrics{First, we used an algorithm introduced by Honda to measure the
  discrepancy of each barrel shape from a Dirichletform shape}
\citep{honda_geometrical_1983}.  \metrics{Low overall values of this
  \emph{Honda-}$\delta$ metric obtained from simulated barrels indicate a
  close correspondence of the simulated barrel field with a Voronoi
  tesselation, and thus with a biological barrel field. For the tesselation
  that is overlaid on the real barrel field in Fig.\,\ref{fig:main}A,
  $\delta=0.025$, and a reduction in $\delta$ in the example simulation over
  time confirmed that an equivalent `good' Voronoi pattern} (see
\citealp{senft_mouse_1991}) \metrics{can emerge within $\approx$~20000
  iterations (Fig.\,\ref{fig:main}D, red circles). Second, we devised a
  \emph{pattern difference} measure that is sensitive to deviations in the
  component shapes and overall topographic registration between two
  tesselations, $\eta$, and we used this measure to compare the simulated
  barrel fields to the real barrel field from which the boundary shape applied
  to the simulation was obtained (see \emph{Materials \& Methods} for
  details). A similar reduction in $\eta$ in the development of the example
  simulation confirmed that the shapes and arrangement of emergent connection
  fields came to match those of the real barrel field by around 20000
  iterations (Fig.\,\ref{fig:main}D, black squares). Third, we measured the
  \emph{connection selectivity} at each location on the cortical sheet, as the
  connection density of the most dense projection divided by the sum over all
  projection densities, $\omega$. The connection selectivity increased as the
  barrel map self-organised in the example simulation (Fig.\,\ref{fig:main}D,
  grey hexagons), and the selectivity became concentrated in regions
  overlapping with the emergent barrel centers (Fig.\,\ref{fig:main}E).}

>>>>

\cmnt{Across a wide range of parameter values, random initial conditions (a
  uniform random distribution for $a(\mb{x},0)\in(0.2,0.4)$, $c(\mb{x},0)=0$)
  eventually yielded a clear Voronoi-like tessellation of topographically
  organized thalamocortical projections, confirming that barrel maps can
  self-organize in the absence of pre-specified center points. The
  organization is apparent in a plot of the identity of the projection for
  which the connection density is maximal at each simulated cortical location,
  as shown in Fig.\,\ref{fig:main}C. Parameters for the example simulation
  shown in Fig.\,\ref{fig:main}C (see also Movie S1) were obtained by
  conducting a full parameter sweep and choosing a combination of parameter
  values ($\alpha=3.6$, $\beta=16.67$, $k=3$, $D=0.5$, $\epsilon=1.2$) that
  scored well against the following three measures.}

% New section to describe and introduce the metrics
\metrics{First, we used an algorithm introduced by Honda to measure the
  discrepancy of each barrel shape from a Dirichletform shape}
\citep{honda_geometrical_1983}.  \metrics{Low overall values of this
  \emph{Honda-}$\delta$ metric obtained from simulated barrels indicate a
  close correspondence of the simulated barrel field with a Voronoi
  tesselation, and thus with a biological barrel field. For the tesselation
  that is overlaid on the real barrel field in Fig.\,\ref{fig:main}A,
  $\delta=0.025$, and a reduction in $\delta$ in the example simulation over
  time confirmed that an equivalent `good' Voronoi pattern} (see
\citealp{senft_mouse_1991}) \metrics{can emerge within $\approx$~20000
  iterations (Fig.\,\ref{fig:main}D, red circles). Second, we devised a
  \emph{pattern difference} measure that is sensitive to deviations in the
  component shapes and overall topographic registration between two
  tesselations, $\eta$, and we used this measure to compare the simulated
  barrel fields to the real barrel field from which the boundary shape applied
  to the simulation was obtained (see \emph{Materials \& Methods} for
  details). A similar reduction in $\eta$ in the development of the example
  simulation confirmed that the shapes and arrangement of emergent connection
  fields came to match those of the real barrel field by around 20000
  iterations (Fig.\,\ref{fig:main}D, black squares). Third, we measured the
  \emph{connection selectivity} at each location on the cortical sheet, as the
  connection density of the most dense projection divided by the sum over all
  projection densities, $\omega$. The connection selectivity increased as the
  barrel map self-organized in the example simulation (Fig.\,\ref{fig:main}D,
  grey hexagons), and the selectivity became concentrated in regions
  overlapping with the emergent barrel centers (Fig.\,\ref{fig:main}E).}
